---
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(arules)
library(arulesViz)
```

```{r}
data(Groceries)
rules <- apriori(Groceries, parameter = list(supp = .004, conf = .3, minlen=2))
```

```{r}
summary(rules)
plot(rules)
inspect(sort(rules, by="support"))
```

Highest Confidence: {other vegetables, yogurt, fruit/vegetable juice} => {whole milk} .6172840
tropical fruit, other vegetables, yogurt --> whole milk .619
citrus fruit --> newspapers .00833
whipped/sour cream --> chicken,napkins,newspaper .00721911
tropical fruit, root vegetables, yogurt --> shole milk .7

Highest Lift: Ham --> white bread | white bread --> ham = 4.639
citrus fruit, other veggies, whole milk --> root veggies 4.0855
herbs --> root veggies 3.9564
citrus fruit, pip fruit --> tropical fruit 3.854
tropical fruit, other vegetables, whole milk --> root veggies 3.768

Highest support: other vegetables --> whole milk .07483
root veggies, whole milk --> other veggies .023
other veggies, rolls/buns --> whole milk .01789
other vegetables --> whole milk .00748
root,other vegetables, yogurt --> whole milk .00783

Most interesting:
tropical fruit, newspapers --> rolls/buns 
sausage, bottled water --> other vegetables
citrus fruit --> newspapers .00833
tropical fruit, curd --> yogurt
yogurt, soda --> rolls/buns


