---
output: html_document
---

```{r setup, include=FALSE}
# Include Libraries
library(tidyverse)
library(DT)

# Import Data
data <- read_csv("r_ensemble.csv")
```

<h1 id="title">Grid Exploration<h1>

<br>

<h1 id="names"> Andrew Wolfe | Jeremy Chandler | Ryan Recanzone</h1>

<br><br>

<p id="desc">The following is a visual report of an grid of many machine learning algorithms, with different combinations of cross validations, dataset size, data types, and individual algorithm parameters.</p>

<br><br>

<h1 id="subtitle">Data</h1>

<br><br>

```{r, echo = FALSE}
# Show datatable
datatable(data, class = 'hover', 
          options = list(pageLength = nrow(data)/24))
```

<br><br>

<h1 id="subtitle">Data Type and K-Folds</h1>

<br><br>

```{r, fig.width=10, fig.height=4, fig.align='center', echo=FALSE}
plot1 <- ggplot(data = data, aes(x = Type, y = Accuracy)) +
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(color = as.factor(Kfolds))) +
  theme_bw() +
  labs(x = "Categorical and Numerical", color = "K Fold Amount") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)))
plot1
```

<br><br>

<h1 id="subtitle">Row Amount</h1>

<br><br>

```{r, fig.width=10, fig.height=4, fig.align='center', echo=FALSE}
plot2 <- ggplot(data = data, aes(x = Row, y = Accuracy)) +
  geom_point(aes(color = as.factor(Kfolds))) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  theme_bw() +
  labs(x = "Amount of Rows", color = "K Fold Amount") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)))
plot2
```

<br><br>

<h1 id="subtitle">Unique Target Amount</h1>

<br><br>

```{r, fig.width=10, fig.height=4, fig.align='center', echo=FALSE}
plot3 <- ggplot(data = data, aes(x = Target, y = Accuracy)) +
  geom_point(aes(color = as.factor(Kfolds))) +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  theme_bw() +
  labs(x = "Amount of Unique Targets", color = "K Fold Amount") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)))
plot3
```

<br><br>

<h1 id="subtitle">Algorithm Comparison Against Chance</h1>

<br><br>

```{r, fig.width=10, fig.height=7, fig.align='center', echo=FALSE}
plot4 <- ggplot(data = data, aes(x = Row, y = Accuracy)) +
  geom_line(aes(y = guessing_chance), color = "red") +
  geom_line(color = "black") +
  facet_wrap(~Algorithm, nrow = 3) +
  theme_bw() +
  labs(x = "Amount of Rows", color = "Accuracy | Probability by Chance") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)))
plot4
```

<br><br>

<h1 id="subtitle">Algorithm Comparison</h1>

<br><br>

```{r, fig.width=10, fig.height=9, fig.align='center', echo=FALSE}
plot5 <- ggplot(data = data, aes(x = Row, y = Accuracy)) +
  geom_point(aes(color = Algorithm)) +
  geom_line(aes(color = name, group = name)) +
  facet_wrap(~Kfolds, nrow = 2) +
  theme_bw() +
  labs(x = "Amount of Rows", color = "Algorithm") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)),
        legend.position="top")
plot5
```

<br><br>

<h1 id="subtitle">Algorithm Comparison</h1>

<br><br>

```{r, fig.width=10, fig.height=4, fig.align='center', echo=FALSE}
plot6 <- ggplot(data = data, aes(x = name, y = Accuracy)) +
  geom_boxplot() +
  geom_jitter(aes(color = Type)) +
  theme_bw() +
  labs(x = "Algorithm", color = "Data Type") +
  theme(axis.title = element_text(size = rel(2)),
        legend.title = element_text(size = rel(1.3)))
plot6
```



<style>
@import url('https://fonts.googleapis.com/css?family=Gugi');
@import url('https://fonts.googleapis.com/css?family=Raleway');
@import url('https://fonts.googleapis.com/css?family=IBM+Plex+Sans');
@import url('https://fonts.googleapis.com/css?family=Muli');
#title{
margin: auto;
text-align: center;
font-size: 70px;
font-family: 'Gugi', cursive;
color: #1A17D1;
}
#names{
margin: auto;
text-align: center;
font-size: 30px;
font-family: 'Raleway', sans-serif;
color: #2C7607;
}
#subtitle{
margin: auto;
text-align: center;
font-size: 50px;
font-family: 'IBM Plex Sans', sans-serif;
color: #590B90;
}
#desc{
font-family: 'Muli', sans-serif;
font-size: 20px;
font-weight: bold;
}
</style>
